Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-05 paper.qmd
Updated Figure 9

```{r}
#| label: five-gau-tsne-projs
projection <- cbind(
  c(-0.00215,-0.68905,-0.04778,-0.54223),
  c(0.42558,-0.23854,-0.63659,0.35753))

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 1, 
               scaled_data = scaled_gau_data, 
               scaled_data_model = scaled_gau_data_model, 
               distance_df_small_edges = tr_from_to_df_gau1, 
               axis_param = list(limits = 1,
                                 axis_scaled = 1,
                                 axis_pos_x = -0.72, 
                                 axis_pos_y = -0.72, 
                                 threshold = 0))

@@

```{r}
#| label: five-gau-umap-projs
projection <- cbind(
  c(-0.00215,-0.68905,-0.04778,-0.54223),
  c(0.42558, -0.23854, -0.63659, 0.35753))

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 1, 
               scaled_data = scaled_gau_data, 
               scaled_data_model = scaled_gau_data_model, 
               distance_df_small_edges = tr_from_to_df_gau1, 
               axis_param = list(limits = 1, 
                                 axis_scaled = 1,
                                 axis_pos_x = -0.72, 
                                 axis_pos_y = -0.72, 
                                 threshold = 0))

@@

```{r}
#| label: five-gau-pacmap-projs
## First projection
projection <- cbind(
  c(-0.00215,-0.68905,-0.04778,-0.54223),
  c(0.42558,-0.23854,-0.63659,0.35753))

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 1, 
               scaled_data = scaled_gau_data, 
               scaled_data_model = scaled_gau_data_model, 
               distance_df_small_edges = tr_from_to_df_gau1, 
               axis_param = list(limits = 1,
                                 axis_scaled = 1,
                                 axis_pos_x = -0.72, 
                                 axis_pos_y = -0.72, 
                                 threshold = 0))

>>>>

```{r}
#| label: five-gau-tsne-projs
projection <- cbind(
  c(0.07108,0.19751,-0.21229,0.26341),
  c(-0.23494,0.27965,-0.01430,-0.15782))

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 2, 
               scaled_data = scaled_gau_data, 
               scaled_data_model = scaled_gau_data_model, 
               distance_df_small_edges = tr_from_to_df_gau1, 
               axis_param = list(limits = 1,
                                 axis_scaled = 2,
                                 axis_pos_x = -0.72, 
                                 axis_pos_y = -0.72, 
                                 threshold = 0.1))

@@

```{r}
#| label: five-gau-umap-projs
projection <- cbind(
  c(0.07108,0.19751,-0.21229,0.26341),
  c(-0.23494,0.27965,-0.01430,-0.15782))

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 2, 
               scaled_data = scaled_gau_data, 
               scaled_data_model = scaled_gau_data_model, 
               distance_df_small_edges = tr_from_to_df_gau1, 
               axis_param = list(limits = 1,
                                 axis_scaled = 2,
                                 axis_pos_x = -0.72, 
                                 axis_pos_y = -0.72, 
                                 threshold = 0.1))

@@

```{r}
#| label: five-gau-pacmap-projs
## First projection
projection <- cbind(
  c(0.07108,0.19751,-0.21229,0.26341),
  c(-0.23494,0.27965,-0.01430,-0.15782))

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 2, 
               scaled_data = scaled_gau_data, 
               scaled_data_model = scaled_gau_data_model, 
               distance_df_small_edges = tr_from_to_df_gau1, 
               axis_param = list(limits = 1,
                                 axis_scaled = 2,
                                 axis_pos_x = -0.72, 
                                 axis_pos_y = -0.72, 
                                 threshold = 0.1))
